---
title: "homework 1"
author: "Rowan"
date: '2022-09-29'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Answer the following questions with dplyr code in RMarkdown. Post the answer into your github as a “nice readme” as explained in class.

How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
These questions come from r4ds. Please turn them in Tuesday (9/27) at 5pm in canvas.

```{r }

library(dplyr)

install.packages("nycflights13")
library(nycflights13)
library(ggplot2)
```

```{r}
# How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
sum(is.na(flights$dep_time))
sum(is.na(flights$dep_delay))
sum(is.na(flights$arr_time))
sum(is.na(flights$arr_delay))
sum(is.na(flights$tailnum))
sum(is.na(flights$air_time))



#8255 flights have missing dep_time. Other variables like dep_delay, arr_time, arr_delay, tailnum, air_time have some missing in those flights.
#These rows have missing data may suggest that some flights were cancelled or occur information missing in the data collection process.





```


```{r}

#Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

Flight_1<-flights%>%
  mutate(dep_time=(dep_time%/%100*60+(dep_time%%100)))%>%
  mutate(sched_dep_time=(sched_dep_time%/%100*60+(sched_dep_time%%100)))
Flight_1

# I convert those time into minutes accumulated since midnight 12 am. For example, 5:17 am is converted into 5*60+17=317 minutes after 12 am.  
```


```{r}
#Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()


flights %>%  
group_by(year, month, day) %>% 
  summarise(
    flight_num = length(dep_time),
    canceled_num=sum(is.na(dep_time)),
    flight_canceled_rate=canceled_num/flight_num,
    avg_delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  ggplot(mapping = aes(y = flight_canceled_rate, x = avg_delay)) + 
  geom_point()

# We can observe a possible pattern between the proportion of canceled flights and the average delay. And it seems that: on a specific day, the higher the average delay time of flights on that day, the more proportion of flights may be cancelled, even though there are a few outliers.

```










